Radar code documentation

### 2022-05-11 doc/msp_code.tex
update doc

\DeclareMathOperator{\sgn}{sgn}
\renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}
\setlength\parindent{0pt}

@@

\section{Introduction}
A novel binary phase radar code is presented which has optimal noise canceling properties for the lag value estimator being considered.
Furthermore, it is shown that the estimator is close to the Cramér–Rao bound.
The code intrinsically measures the entire range at once, which must be finite.
\section{Estimator and code requirement for zero bias}
We assume that the radar code $\epsilon$ has length $L$ and is periodic $\epsilon_i = \epsilon_{i + L}$.
Furthermore, the radar code is normalized and binary phase, meaning that $\epsilon_i \in [-1, 1]$.
This implies that $\epsilon_i^*\epsilon_i = 1$, where we could drop the complex conjugate symbol, but we will keep it to show that the formalism also applies to poly-phase codes.
We further assume that the radar code is transmitted indefinitely.\\
Figure \ref{fig:sketch} illustrates the measurement process of the unmodulated code.
In the figure, it can be seen that the measured voltage $m_i$ at time index $i$ can be calculated by summing over the scattered voltages $V^{(k)}_i$ which are modulated with the radar code,
\begin{equation}
m_i = \sum_{k=0}^{N-1} \epsilon_{i-k} V^{(k)}_i
\end{equation}
where $N$ is the maximum altitude index considered and $k$ is the altitude index.
Note that $N$ must be finite.\\
Now, the estimator
\begin{equation}
\hat{R}^{(h)}_\Delta = \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j + \Delta}m_{j + \Delta + h}^* \epsilon_j^*m_{j + h}.
\end{equation}
for the autocorrelation function $R$ at altitude $h$ and lag $\Delta > 0$ is introduced.
In the following, it will be shown that this estimator is unbiased, if the code fulfills a certain condition.\\
We calculate the expectation value of the estimator
\begin{equation}
\langle \hat{R}^{(h)}_\Delta \rangle
=\frac{1}{L}\sum^{L - 1}_{j=0} \epsilon_{j + \Delta}\epsilon_j^* \sum_{k=0}^{N-1} \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} \langle (V^{(k)}_{j + \Delta})^*V^{(k)}_j \rangle
\end{equation}
where the double sum was reduced to a single sum symbol, because scattered voltages of different altitudes do not correlate.
Now, we use the definition of the autocorrelation function $\langle (V_{j+\Delta}^{(k)})^* V_j^{(k)} \rangle = R^{(k)}_\Delta$, where we assume a wide sense stationary process during the time it takes to transmit the code once.
\begin{equation}
\langle \hat{R}^{(h)}_\Delta \rangle
= R^{(h)}_\Delta + \sum_{k=0,k\neq h}^{N-1}R^{(k)}_\Delta
\left[ \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j + \Delta}\epsilon_j^* \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k}\right].
\end{equation}
The estimator is unbiased if the expression in the square brackets is zero.
Let $w = k - h$ and note that $w \neq 0$ and $|w| < N$.
Using the periodicity it can be shown that the condition is equivalent to
\begin{equation}
0 = \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j}\epsilon_{j+w}^* \epsilon_{j+\Delta}^*\epsilon_{j + \Delta + w}.
\label{eq:cond}
\end{equation}
\subsection{Bias of a random code}
For a random code, the condition is not exactly zero
\begin{equation}
r = \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j}\epsilon_{j+w}^* \epsilon_{j+\Delta}^*\epsilon_{j + \Delta + w}.
\end{equation}
The variance is
\begin{equation}
\mathrm{Var}[r] = \frac{1}{L},
\end{equation}
which means that the result will be biased on average by
\begin{equation}
b^{(h)}_\Delta = \sum_{k=0,k\neq h}^{N-1}\frac{R^{(k)}_\Delta}{\sqrt{L}}
\end{equation}

@@

@@

@@

\section{Modulating the code}
\subsection{Modulation with fixed code}

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{code_diagram_modulated.pdf}
	\caption{Range time diagram of the modulated version of the radar code with $S=3$.}
	\label{fig:modulated}
\end{figure}
m_{i,w} = \sum_{k=0}^{N-1} \epsilon_{i-k} \sum_{s=0}^{S-1} \gamma_{S-1-s} V^{(k, s + w)}_{i}
d_{i,w} = \sum^{S-1}_{s=0} \gamma_{s} m_{i, s + w}
d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k} \sum_{s_1=0}^{S-1} \sum^{S-1}_{s_2=0} \gamma_{s_2} \gamma_{S-1-s_1} V_i^{(k, s_1 + s_2 + w)}
d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k} \sum_{s_1=0}^{S-1} \sum^{S-1}_{s_2=0} \gamma_{s_1} \gamma_{s_2} V_i^{(k, S - 1 - s_1 + s_2 + w)}
d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k}\left[SV_i^{(k, S - 1 + w)}
+ \sum_{s_1=1}^{S-1} \sum^{S-1-s_1}_{s_2=0} \gamma_{s_2} \gamma_{s_1 + s_2} V_i^{(k, S - 1 + s_1 + w)}
+ \sum_{s_1=1}^{S-1} \sum^{S-1-s_1}_{s_2=0} \gamma_{s_2+s_1} \gamma_{s_2} V_i^{(k, S - 1 - s_1 + w)} \right]
A_{s_1} = \sum^{S-1-s_1}_{s_2=0} \gamma_{s_2+s_1} \gamma_{s_2}\text{ for }s_1\in[0, S-1]
d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k}\sum_{s=1-S}^{S-1} A_{|s|} V_i^{(k, S - 1 + s + w)}
\hat{R}^{(h, w)}_\Delta = \frac{1}{L}\sum^{L-1}_{j=0}
\epsilon_{j + \Delta}d_{j + \Delta + h, w}^*
\epsilon_jd_{j + h, w}.
\hat{R}^{(h, w)}_\Delta = \frac{1}{L}\sum^{L-1}_{j=0}
\epsilon_{j + \Delta}
\sum_{k_1=0}^{N-1}\epsilon_{j+\Delta+h-k_1}\sum_{s_1=1-S}^{S-1} A_{|s_1|} \left(V_{j+\Delta+h}^{(k_1, S - 1 + s_1 + w)}\right)^*
\epsilon_j
\sum_{k_2=0}^{N-1}\epsilon_{j+h-k_2}\sum_{s_2=1-S}^{S-1} A_{|s_2|} V_{j+h}^{(k_2, S - 1 + s_2 + w)}
\langle \hat{R}^{(h, w)}_\Delta \rangle = \frac{1}{L}\sum^{L-1}_{j=0}
\epsilon_{j + \Delta}
\sum_{k=0}^{N-1}\epsilon_{j+\Delta+h-k}\sum_{s_1=1-S}^{S-1} A_{|s_1|} 
\epsilon_j
\epsilon_{j+h-k}\sum_{s_2=1-S}^{S-1} A_{|s_2|} \left\langle \left(V_{j+\Delta+h}^{(k, S - 1 + s_1 + w)}\right)^* V_{j+h}^{(k, S - 1 + s_2 + w)} \right\rangle
\left\langle \left(V_{j+\Delta+h}^{(k, S - 1 + s_1 + w)}\right)^* V_{j+h}^{(k, S - 1 + s_2 + w)} \right\rangle =
\delta_{s_1, s_2} R_\Delta^{(k, S-1+s_1+w)} +
\delta_{s_1, s_2+1} R_\Delta^{(k, S-1+s_1+w + 0.5)}/2 +
\delta_{s_1, s_2-1} R_\Delta^{(k, S-1+s_1+w - 0.5)}/2
\langle \hat{R}^{(h, w)}_\Delta \rangle =
\sum_{s_1=1-S}^{S-1} A^2_{|s_1|}R_\Delta^{(h, S-1+s_1+w)}+
\frac{1}{2}\sum_{s_1=1-S}^{S-2} A_{|s_1|}A_{|s_1+1|}R_\Delta^{(h, S-1+s_1+w+0.5)}+
\frac{1}{2}\sum_{s_1=2-S}^{S-1} A_{|s_1|}A_{|s_1-1|}R_\Delta^{(h, S-1+s_1+w-0.5)}
if $\gamma$ is a barker code we have $A_{|i|}A_{|i+1|}=0$
\langle \hat{R}^{(h, w)}_\Delta \rangle =
\sum_{s_1=1-S}^{S-1} A^2_{|s_1|}R_\Delta^{(h, S-1+s_1+w)}
so we find a biased estimator, where the signal is stronger by a factor
\frac{S^2}{S - 1}
compared to the bias.
one can also deconvolute, to find an exact result.
\subsection{Modulation with variable code}
\subsection{Hypothesis on code length}
\section{Code with cyclic difference set for $\tau_i$}
\section{Simulation}
\subsection{Monte Carlo Generation}
The most straight-forward approach to generate random numbers following a wide-sense stationary process is as follows:
R^{(h)}_{jk} = \langle (V_{j}^{(h)})^* V_k^{(h)} \rangle
where $R^{(h)}_{jk}$ is interpreted (for some fixed $h$) as a correlation matrix for the random vector $V_{j}^{(h)}$ which is to be generated.
We can satisfy the correlation properties by a linear transformation
V_j^{(h)} = \sum_{i} T_{ji}f_i
where $T_{ji}$ must be of toeplitz type and $f_i$ are uncorrelated standard normal Gaussian circular-symmetric random variables with $\langle f_i f_j \rangle = \delta_{ij}$.
This yields
R^{(h)}_{jk} = \sum_{i,l} \langle (T_{ji}f_i)^* T_{kl}f_l \rangle = \sum_{i} T_{ji}^* T_{ki}.
Using that the matrix $T$ is symmetric and seeing that $R^{(h)}_{jk}$ must be positive semidefinite (as it is a covariance matrix) we can calculate $T$ with some square root of matrix algorithm.\\
However all of this can be done more efficiently by using the time stationary of the process.
Note that $T$ is of toeplitz type simply means that we actually need a convolution of $f$ with $T$ where $T$ must be symmetric with a length of at least $2M + 1$ so that the points up to $M + 1$ can be correlated.
However, the generated time series would not have the true correlation properties of the ACF if it is truncated after $M+1$.
The ACF can be either truncated after $n-1$, where $n$ is the total length of the time series, or when the ACF approaches approximately zero.
Now, denote the length of the ACF by $K$.
The convolution is given by
V_j^{(h)} = \sum_{i=1-K}^{K-1} T_{i}f_{j - i}.
It follows that,
R^{(h)}_{jk} = \langle (V_{j}^{(h)})^* V_k^{(h)} \rangle = \sum_{l=1-K}^{K-1} \sum_{m=1 - K}^{K-1} T_{l} T_{m} \langle f_{j - l} f_{k - m} \rangle.
Using that $\langle f_{j - l} f_{k - m} \rangle = \delta_{m, k - j + l}$ and substituting $\Delta=j-k$ yields
R^{(h)}_\Delta = \sum_{i=1-K}^{K-1} T_{i} T_{i - \Delta}
where it is assumed that $T$ is zero padded for all indices which fall out of range.
Applying a Fourier transform over $\Delta$ on both sides results in
\mathrm{DCT}[R^{(h)}]_j = \sum_{i=1-K}^{K-1} T_{i}\mathrm{DTFT}[T_{i - \Delta}]_j.
From the definition of the $\mathrm{DTFT}$ follows that
\mathrm{DCT}[R^{(h)}]_j = \sum_{l=1-K}^{K-1} T_{l}\exp\left(\frac{i2\pi lj}{2K-1} \right) \mathrm{DCT}[T]_j,
using the definition of the Fourier transform again results in
\mathrm{DCT}[R^{(h)}]_j = (2K - 1)\left( \mathrm{DCT}[T]_j \right)^2.
Now there are two options: Either one solves for $T$ and does the convolution in the time domain, or one solves for the Fourier transform of $T$ and does the convolution in Fourier space.
Which one is faster depends on the choice of $K$.
The first approach is preferred when $K$ is fixed which results in an asymptotic runtime of $\mathcal{O}(Kn)$.
In the case $K=n$ latter approach is preferred as it results in a runtime of $\mathcal{O}(n\log(n))$.
However, choosing $K=n$ has not a real practical use case, as the ACF can always be cut off at small value, in the sense that $M \gtrsim K$.

>>>>

\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Cov}{Cov}
\renewcommand{\Re}{\mathrm{Re}}
\renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}
\setlength\parindent{0pt}

@@

\section{Introduction}
A novel binary phase radar code is presented which has optimal noise canceling properties for the lag value estimator being considered.
Furthermore, it is shown that the estimator is close to the Cramér–Rao bound.
The code intrinsically measures the entire range at once, which must be finite.
\section{Estimator and code requirement for zero bias}
We assume that the radar code $\epsilon$ has length $L$ and is periodic $\epsilon_i = \epsilon_{i + L}$.
Furthermore, the radar code is normalized and binary phase, meaning that $\epsilon_i \in [-1, 1]$.
This implies that $\epsilon_i^*\epsilon_i = 1$, where we could drop the complex conjugate symbol, but we will keep it to show that the formalism also applies to poly-phase codes.
We further assume that the radar code is transmitted indefinitely.\\
Figure \ref{fig:sketch} illustrates the measurement process of the unmodulated code.
In the figure, it can be seen that the measured voltage $m_i$ at time index $i$ can be calculated by summing over the scattered voltages $V^{(k)}_i$ which are modulated with the radar code,
\begin{equation}
m_i = \sum_{k=0}^{N-1} \epsilon_{i-k} V^{(k)}_i
\end{equation}
where $N$ is the maximum altitude index considered and $k$ is the altitude index.
Note that $N$ must be finite.\\
Now, the estimator
\begin{equation}
\hat{R}^{(h)}_\Delta = \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j + \Delta}m_{j + \Delta + h}^* \epsilon_j^*m_{j + h}.
\end{equation}
for the autocorrelation function $R$ at altitude $h$ and lag $\Delta > 0$ is introduced.
In the following, it will be shown that this estimator is unbiased, if the code fulfills a certain condition.\\
We calculate the expectation value of the estimator
\begin{equation}
\langle \hat{R}^{(h)}_\Delta \rangle
=\frac{1}{L}\sum^{L - 1}_{j=0} \epsilon_{j + \Delta}\epsilon_j^* \sum_{k=0}^{N-1} \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} \langle (V^{(k)}_{j + \Delta})^*V^{(k)}_j \rangle
\end{equation}
where the double sum was reduced to a single sum symbol, because scattered voltages of different altitudes do not correlate.
Now, we use the definition of the autocorrelation function $\langle (V_{j+\Delta}^{(k)})^* V_j^{(k)} \rangle = R^{(k)}_\Delta$, where we assume a wide sense stationary process during the time it takes to transmit the code once.
\begin{equation}
\langle \hat{R}^{(h)}_\Delta \rangle
= R^{(h)}_\Delta + \sum_{k=0,k\neq h}^{N-1}R^{(k)}_\Delta
\left[ \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j + \Delta}\epsilon_j^* \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k}\right].
\end{equation}
The estimator is unbiased if the expression in the square brackets is zero.
Let $w = k - h$ and note that $w \neq 0$ and $|w| < N$.
Using the periodicity it can be shown that the condition is equivalent to
\begin{equation}
0 = \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j}\epsilon_{j+w}^* \epsilon_{j+\Delta}^*\epsilon_{j + \Delta + w}.
\label{eq:cond}
\end{equation}
\subsection{Bias of a random code}
For a random code, the condition is not exactly zero
\begin{equation}
r = \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j}\epsilon_{j+w}^* \epsilon_{j+\Delta}^*\epsilon_{j + \Delta + w}.
\end{equation}
The variance is
\begin{equation}
\mathrm{Var}[r] = \frac{1}{L},
\end{equation}
which means that the result will be biased on average by
\begin{equation}
b^{(h)}_\Delta = \sum_{k=0,k\neq h}^{N-1}\frac{R^{(k)}_\Delta}{\sqrt{L}}
\end{equation}
However, one would use deconvolution (lag profile inversion) for a random code, this would remove the bias.

@@

\section{Covariance with correct calculation of real part - also use this for variance}

\begin{equation}
\left \langle
\Re\left(\hat{R}^{(h)}_{\Delta_1}\right)
\Re\left(\hat{R}^{(h)}_{\Delta_2}\right)
\right \rangle =
\frac{1}{L^2}\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}
\epsilon_{j_1} \epsilon_{j_1 + \Delta_1}
\epsilon_{j_2} \epsilon_{j_2 + \Delta_2}
\left\langle
\Re\left(m_{j_1 + \Delta_1 + h} m_{j_1 + h}^*\right)
\Re\left(m_{j_2 + \Delta_2 + h}^* m_{j_2 + h}\right)
\right\rangle
\end{equation}

\begin{equation*}
\begin{split}
2\left\langle
\Re\left(m_{j_1 + \Delta_1 + h}m_{j_1 + h}^*\right)
\Re\left(m_{j_2 + \Delta_2 + h}^* m_{j_2 + h}\right)
\right\rangle
= \: &
\Re\left(\left\langle m_{j_1 + \Delta_1 + h} m_{j_1 + h}^* m_{j_2 + \Delta_2 + h}^* m_{j_2 + h}\right\rangle\right)+ \\&
\Re\left(\left\langle m_{j_1 + \Delta_1 + h}^* m_{j_1 + h} m_{j_2 + \Delta_2 + h}^* m_{j_2 + h}\right\rangle\right)
\end{split}
\end{equation*}

plugged into the previous expression this gives

\begin{equation*}
\begin{split}
\left \langle
\Re\left(\hat{R}^{(h)}_{\Delta_1}\right)
\Re\left(\hat{R}^{(h)}_{\Delta_2}\right)
\right \rangle = \: &
\frac{1}{2}\Re\left(\left\langle\hat{R}^{(h)}_{\Delta_1}\right\rangle^* \left\langle\hat{R}^{(h)}_{\Delta_2} \right\rangle\right)+
\frac{1}{2}\Re\left(\left\langle\hat{R}^{(h)}_{\Delta_1}\right\rangle \left\langle\hat{R}^{(h)}_{\Delta_2} \right\rangle\right)+ \\&
\frac{1}{2L^2}\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}
\epsilon_{j_1} \epsilon_{j_1 + \Delta_1}
\epsilon_{j_2} \epsilon_{j_2 + \Delta_2}
A
\end{split}
\end{equation*}

\begin{equation*}
A = \Re\left(\left
\langle m_{j_2 + \Delta_2 + h}^* m_{j_1 + \Delta_1 + h} \rangle
\langle m_{j_1 + h}^* m_{j_2 + h} \rangle
\right\rangle\right) +
\Re\left(\left
\langle m_{j_1 + \Delta_1 + h}^* m_{j_2 + h} \rangle
\langle m_{j_2 + \Delta_2 + h}^* m_{j_1 + h} \rangle
\right\rangle\right)
\end{equation*}

\begin{equation*}
\Cov\left[
\Re\left( \hat{R}^{(h)}_{\Delta_1} \right),
\Re\left( \hat{R}^{(h)}_{\Delta_2} \right)
\right] = \frac{1}{2L^2}\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}
\epsilon_{j_1} \epsilon_{j_1 + \Delta_1}
\epsilon_{j_2} \epsilon_{j_2 + \Delta_2}
A
\end{equation*}

\begin{equation*}
\hat{\epsilon}_{j, \Delta, l_1, l_2} = \epsilon_j \epsilon_{j + \Delta} \epsilon_{j + h - l_2} \epsilon_{j + \Delta + h - l_1}
\end{equation*}

\begin{equation*}
\Cov\left[
\Re\left( \hat{R}^{(h)}_{\Delta_1} \right),
\Re\left( \hat{R}^{(h)}_{\Delta_2} \right)
\right] = \frac{1}{2L^2}
\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}
\sum_{k_1=0}^{N-1}\sum_{k_2=0}^{N-1}\left(A+B\right)
\end{equation*}

\begin{align}
A &= \hat{\epsilon}_{j_1, \Delta_1, k_1, k_2}\hat{\epsilon}_{j_2, \Delta_2, k_1, k_2}
\Re\left( R^{(k_1)}_{j_2 - j_1 + \Delta_2 - \Delta_1}R^{(k_2)}_{j_2 - j_1} \right)\\
B &= \hat{\epsilon}_{j_1, \Delta_1, k_1, k_2}\hat{\epsilon}_{j_2, \Delta_2, k_2, k_1}
\Re\left( R^{(k_1)}_{j_1 - j_2 + \Delta_1}R^{(k_2)}_{j_2 - j_1 + \Delta_2} \right)
\end{align}

@@

5 3 2 5 4

for s >= 0:
5: -min(s, 3)
3: -min(s, 2)
2: -min(s, 2)
4: -min(s, 4) + min(s - 5, 0)

@@

\section{Modulating the code}
\subsection{Modulation with fixed code, match filter on pulse, ignoring voltage changes}
In the following it is considered that the recieved modulated voltage is demodulated first with an inverse filter and then correlated.
This leads to a nice analytical expression, but only if the voltage during one pulse is condidered constant, which is wrong...
\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{code_diagram_modulated.pdf}
	\caption{Range time diagram of the modulated version of the radar code with $S=3$.}
	\label{fig:modulated}
\end{figure}
\begin{equation}
m_{i,w} = \sum_{k=0}^{N-1} \epsilon_{i-k} \sum_{s=0}^{S-1} \gamma_{S-1-s} V^{(k, s + w)}_{i}
\end{equation}
\begin{equation}
d_{i,w} = \sum^{S-1}_{s=0} \gamma_{s} m_{i, s + w}
\end{equation}
\begin{equation}
w \in [0, K - S]
\end{equation}
Where $K$ is the number of bits received.
\begin{equation}
d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k} \sum_{s_1=0}^{S-1} \sum^{S-1}_{s_2=0} \gamma_{s_2} \gamma_{S-1-s_1} V_i^{(k, s_1 + s_2 + w)}
\end{equation}
\begin{equation}
d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k} \sum_{s_1=0}^{S-1} \sum^{S-1}_{s_2=0} \gamma_{s_1} \gamma_{s_2} V_i^{(k, S - 1 - s_1 + s_2 + w)}
\end{equation}
\begin{equation}
d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k}\left[SV_i^{(k, S - 1 + w)}
+ \sum_{s_1=1}^{S-1} \sum^{S-1-s_1}_{s_2=0} \gamma_{s_2} \gamma_{s_1 + s_2} V_i^{(k, S - 1 + s_1 + w)}
+ \sum_{s_1=1}^{S-1} \sum^{S-1-s_1}_{s_2=0} \gamma_{s_2+s_1} \gamma_{s_2} V_i^{(k, S - 1 - s_1 + w)} \right]
\end{equation}
\begin{equation}
A_{s_1} = \sum^{S-1-s_1}_{s_2=0} \gamma_{s_2+s_1} \gamma_{s_2}\text{ for }s_1\in[0, S-1]
\end{equation}
\begin{equation}
d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k}\sum_{s=1-S}^{S-1} A_{|s|} V_i^{(k, S - 1 + s + w)}
\end{equation}
\begin{equation}
\hat{R}^{(h, w)}_\Delta = \frac{1}{L}\sum^{L-1}_{j=0}
\epsilon_{j + \Delta}d_{j + \Delta + h, w}^*
\epsilon_jd_{j + h, w}
\end{equation}
\begin{equation}
\hat{R}^{(h, w)}_\Delta = \frac{1}{L}\sum^{L-1}_{j=0}
\epsilon_{j + \Delta}
\sum_{k_1=0}^{N-1}\epsilon_{j+\Delta+h-k_1}\sum_{s_1=1-S}^{S-1} A_{|s_1|} \left(V_{j+\Delta+h}^{(k_1, S - 1 + s_1 + w)}\right)^*
\epsilon_j
\sum_{k_2=0}^{N-1}\epsilon_{j+h-k_2}\sum_{s_2=1-S}^{S-1} A_{|s_2|} V_{j+h}^{(k_2, S - 1 + s_2 + w)}
\end{equation}
\begin{equation}
\langle \hat{R}^{(h, w)}_\Delta \rangle = \frac{1}{L}\sum^{L-1}_{j=0}
\epsilon_{j + \Delta}
\sum_{k=0}^{N-1}\epsilon_{j+\Delta+h-k}\sum_{s_1=1-S}^{S-1} A_{|s_1|} 
\epsilon_j
\epsilon_{j+h-k}\sum_{s_2=1-S}^{S-1} A_{|s_2|} \left\langle \left(V_{j+\Delta+h}^{(k, S - 1 + s_1 + w)}\right)^* V_{j+h}^{(k, S - 1 + s_2 + w)} \right\rangle
\end{equation}
\begin{equation}
\left\langle \left(V_{j+\Delta+h}^{(k, S - 1 + s_1 + w)}\right)^* V_{j+h}^{(k, S - 1 + s_2 + w)} \right\rangle =
\delta_{s_1, s_2} R_\Delta^{(k, S-1+s_1+w)} +
\delta_{s_1, s_2+1} R_\Delta^{(k, S-1+s_1+w + 0.5)}/2 +
\delta_{s_1, s_2-1} R_\Delta^{(k, S-1+s_1+w - 0.5)}/2
\end{equation}
\begin{equation}
\langle \hat{R}^{(h, w)}_\Delta \rangle =
\sum_{s_1=1-S}^{S-1} A^2_{|s_1|}R_\Delta^{(h, S-1+s_1+w)}+
\frac{1}{2}\sum_{s_1=1-S}^{S-2} A_{|s_1|}A_{|s_1+1|}R_\Delta^{(h, S-1+s_1+w+0.5)}+
\frac{1}{2}\sum_{s_1=2-S}^{S-1} A_{|s_1|}A_{|s_1-1|}R_\Delta^{(h, S-1+s_1+w-0.5)}
\end{equation}
if $\gamma$ is a Barker code we have $A_{|i|}A_{|i+1|}=0$
\begin{equation}
\langle \hat{R}^{(h, w)}_\Delta \rangle =
\sum_{s_1=1-S}^{S-1} A^2_{|s_1|}R_\Delta^{(h, S-1+s_1+w)}
\end{equation}
so we find a biased estimator, where the signal is stronger by a factor
\begin{equation}
\frac{S^2}{S - 1}
\end{equation}
compared to the bias.
one can also deconvolute, to find an exact result.

\subsection{Modulation with fixed code, match filter on pulse}
\begin{equation}
m_{i,w} = \sum_{k=0}^{N-1} \epsilon_{i-k} \sum_{s=0}^{S-1} \gamma_{S-1-s} V^{(k, s + w)}_{i, w}
\end{equation}
\begin{equation}
d_{i,w} = \sum^{S-1}_{s=0} \gamma_{s} m_{i, s + w}
\end{equation}
\begin{equation}
w \in [0, K - S]
\end{equation}
Where $K$ is the number of bits received.
\begin{equation}
d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k} \sum_{s_1=0}^{S-1} \sum^{S-1}_{s_2=0} \gamma_{s_2} \gamma_{S-1-s_1} V_{i,w+s_2}^{(k, s_1 + s_2 + w)}
\end{equation}

\begin{equation}
d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k} \sum_{s_1=0}^{S-1} \sum^{S-1}_{s_2=0} \gamma_{s_1} \gamma_{s_2} V_{i,w+s_2}^{(k, S - 1 - s_1 + s_2 + w)}
\end{equation}
In order to get rid of half overlapping range gates we use
\begin{equation}
V^{(k,s)}_{i,w} = X^{(L, k, s)}_{i,w} + X^{(U, k, s + 1)}_{i,w}
\end{equation}
with
\begin{equation}
\left\langle \left( X^{(z_1, k, s_1)}_{i_1,w_1} \right)^* X^{(z_2, k, s_2)}_{i_2,w_2} \right\rangle = \delta_{s_1,s_2}G^{(z_1, z_2, k, s_1)}_{\Delta, w_1 - w_2}
\end{equation}
with this we have
\begin{align}
\left \langle \left(V_{i_1,w_1+s_2}^{(k, S - 1 - s_1 + s_2 + w_1)} \right)^* V_{i_2,w_2+s_4}^{(k, S - 1 - s_3 + s_4 + w_2)} \right\rangle =\\
G^{(L, L, S-1-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} \delta_{s_2 - s_1 + w_1, s_4 - s_3 + w_2}\\
+G^{(U, U, S-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} \delta_{s_2 - s_1 + w_1, s_4 - s_3 + w_2}\\
+G^{(L, U, S-1-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} \delta_{s_2 - s_1 + w_1, s_4 - s_3 + w_2 + 1}\\
+G^{(U, L, S-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} \delta_{s_2 - s_1 + w_1 + 1, s_4 - s_3 + w_2}
\end{align}
\begin{align}
\left \langle \left(V_{i_1,w_1}^{(k, s_1)} \right)^* V_{i_2,w_2}^{(k, s_2)} \right\rangle=
\left( G^{(L, L, s_1)}_{\Delta, \delta} + G^{(U, U, s_1 + 1)}_{\Delta, \delta} \right) \delta_{s_1, s_2} + G^{(L, U, s_1)}_{\Delta, \delta} \delta_{s_1, s_2 + 1} + G^{(U, L, s_1 + 1)}_{\Delta, \delta} \delta_{s_1 + 1, s_2}
\end{align}

we see that
\begin{equation}
\left( G^{(z_1, z_2, k, s_1)}_{i, w_1 - w_2} \right)^* = G^{(z_2, z_1, k, s_1)}_{i, w_1 - w_2}
\end{equation}
using this we have
\begin{align}
\left \langle \left(V_{i_1,w_1+s_2}^{(k, S - 1 - s_1 + s_2 + w_1)} \right)^* V_{i_2,w_2+s_4}^{(k, S - 1 - s_3 + s_4 + w_2)} \right\rangle =\\
\left( G^{(U, U, S-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} + G^{(L, L, S-1-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} \right) \delta_{s_2 - s_1 + w_1, s_4 - s_3 + w_2}\\
+G^{(L, U, S-1-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} \delta_{s_2 - s_1 + w_1, s_4 - s_3 + w_2 + 1}\\
+\left( G^{(L, U, S-s_1+s_2+w_1)}_{\Delta, w_1 - w_2 + s_2 - s_4} \right)^* \delta_{s_2 - s_1 + w_1 + 1, s_4 - s_3 + w_2}
\end{align}
\subsection{Modulation with fixed code, decoding first}
\begin{equation}
\langle m_{i_1, w_1}^* m_{i_2, w_2}\rangle = \sum_{s_1=0}^{S-1}\sum_{s_2=0}^{S-1} \gamma_{s_1} \gamma_{s_2} \left\langle \left( V^{(k, S-1-s_1 + w_1)}_{i_1, w_1} \right)^* V^{(k, S-1-s_2 + w_2)}_{i_2, w_2} \right \rangle
\end{equation}

\subsection{Modulation with alternating code}
\begin{equation}
m_{i,w} = \sum_{k=0}^{N-1} \epsilon_{i-k} \sum_{s=0}^{S-1} \gamma^{(k)}_{S-1-s} V^{(k, s + w)}_{i}
\end{equation}
\begin{equation}
\hat{R}^{(h, w)}_\Delta = \frac{1}{L}\sum^{L-1}_{j=0}
\epsilon_{j + \Delta}m_{j + \Delta + h, w}^*
\epsilon_jm_{j + h, w}
\end{equation}

\begin{equation}
\langle \hat{R}^{(h, w)}_\Delta \rangle = \frac{1}{L}
\sum_{s_1=0}^{S-1}
\sum_{s_2=0}^{S-1}
\sum^{L-1}_{j=0}
\sum_{k=0}^{N-1}
\epsilon_{j + \Delta}
\epsilon_{j + \Delta + h - k}\gamma^{(j + \Delta + h - k)}_{S-1-s_1}
\epsilon_j
\epsilon_{i - k} \gamma^{(j + h - k)}_{S-1-s_2}
\langle \left(V^{(k, s_1 + w)}_{j + \Delta + h}\right)^* V^{(k, s_2 + w)}_{j+h} \rangle
\end{equation}
